
\begin{frame}{More information}
    \framesubtitle{CI / CD for Computational Science and Engineering} 

    \begin{itemize}
        \item Maric, Tomislav, Tolle, Tobias, Lehr, Jan-Patrick, Pappagianidis, Ioannis, Bothe, Dieter, \& Bischof, Christian. (2021, September 22). "Continuous" Integration of Scientific Software (in Computational Science and Engineering). High Performance Computing in Hessen (HiPerCH), Darmstadt, Germany. Zenodo. \href{https://doi.org/10.5281/zenodo.5522820}{https://doi.org/10.5281/zenodo.5522820}
        \item \href{https://nfdi4ing.pages.rwth-aachen.de/knowledge-base}{\textbf{NFDI4Ing Knowledgebase}} started from \href{https://www.sfb1194.tu-darmstadt.de/index.en.jsp}{\textbf{CRC 1194 - Z-INF}}, now in cooperation with \textbf{TA Alex} (\href{https://www.fst.tu-darmstadt.de/fachgebiet/mitarbeiter/mitarbeiterdetails_fst_190208.de.jsp}{Michaela Leštáková}) and \textbf{\href{https://www.informatik.tu-darmstadt.de/sc/fg/index.en.jsp}{Scientific Computing} / NFDI4Ing} (\href{https://www.informatik.tu-darmstadt.de/sc/fg/people/details/moritz_schwarzmeier.en.jsp}{Moritz Schwarzmeier (NFDI4Ing S2)}, \href{https://www.informatik.tu-darmstadt.de/sc/fg/people/details/jan_patrick_lehr.en.jsp}{Jan-Patrick Lehr}, \href{https://www.iws.uni-stuttgart.de/en/institute/team/Glaeser-00002/}{Dennis Gläser}), \textbf{Hydraulic Engineering} (\href{https://www.wasserbau.tu-darmstadt.de/wasserbau/fachgebiet_wabau/team_wabau/Details_108736.de.jsp}{Jessika Gappisch})

        \begin{itemize}
            \item CI / CD for CSE research software. 
            \item How-tos and tutorials.  
            \item Minimal Working Examples (MWE) in different programming languages.
            \item Best-practice examples for simulative and experimental projects.
        \end{itemize}

        \textbf{Join the effort, \href{https://git.rwth-aachen.de/nfdi4ing/knowledge-base}{fork the project} and submit merge requests!}\\
    \end{itemize}

\end{frame}
