\section{Workflow overview}

\begin{frame}{A workflow for increasing the quality of scientific CSE software} 

    \vfill
    The workflow is using GitLab, specifically \href{https://git.rwth-aachen.de/}{TUGitLab}. 
    Optional steps are in round () brackets.
    \begin{enumerate}
        \item Track the issues in a Kanban board. 
            \begin{itemize}
                \item Model issues as \href{https://betterscientificsoftware.github.io/PSIP-Tools/PTCs/}{Progress Tracking Cards}\footnote{Developed by \href{https://bssw.io/}{Better Scientific Software.}}.
            \end{itemize}
        \item Use version-control with a simple branching model. 
        \item (Apply Test-Driven Development (TDD) for CSE software.)
        \item (Enable Continuous Integration with an emphasis on result visualization.) 
        \item Cross-link software, result data, and report/article when reaching a milestone.
            \begin{itemize}
                \item When submitting a publication to peer-review. 
                \item After the publication has been accepted. 
                \item When giving up on an idea. 
            \end{itemize}
        \item (Publish a Singularity image with the code and data.)
    \end{enumerate}
\end{frame}

\begin{frame}{A workflow for increasing the quality of (academic) CSE software} 
    \framesubtitle{OpenFOAM}

        \vfill

        The workflow is developed with OpenFOAM projects but it is tested with other software. 

        \vspace{1cm}

        \textbf{Disclaimer}: This offering is not approved or endorsed by OpenCFD Limited, producer and distributor of the OpenFOAM software via www.openfoam.com, and owner of the OPENFOAM®  and OpenCFD®  trade marks. 

\end{frame}
